MSDS6372Project1

### 2021-02-01 MSDS6372Project1.Rmd
objective 2 LogMSRP vs Degree2 EngineHP converting

########################################
# Try LASSO variable selection #########
########################################
library(glmnet)
#Dummy code categorical predictor variables
x <- model.matrix(MSRP~.,train)[,-1]
y <- train$MSRP
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out)
# Look at the coefficient for best lambda
# Make+Model+Year+EngineFuelType+EngineHP+EngineCylinders+TransmissionType+DrivenWheels+NumberOfDoors+VehicleSize+VehicleStyle+HighwayMPG+CityMPG+Popularity+Crossover+Diesel+Exotic+Luxury+HighPerformance+FactoryTurner+Performance+FlexFuel+Hatchback+Hybrid+Yes+N_A
# Lasso turned off some predictors in Make, Model,VehicleStyle... In order to check assumptions, we need to use lm model with all the predictors
# Although this won't imitate the Lasso model perfectly though.
coefficients = coef(cv.out, cv.out$lambda.min)
head(coefficients)
# Compute the final lasso model
lasso.model = glmnet(x,y,alpha = 1,lambda = cv.out$lambda.min)
# Check assumptions

#Dummy code test set to see performance compare to other methods
xtest<-model.matrix(MSRP~.,test)[,-1]
ytest<-test$MSRP #36302210

# See prediction
lasso.pred=predict(lasso.model ,newx=xtest)
# See test ASE
testMSE_LASSO<-mean((ytest-lasso.pred)^2)
testMSE_LASSO

@@

>>>>

########################################
# Try LASSO variable selection #########
########################################
library(glmnet)
#Dummy code categorical predictor variables
x <- model.matrix(MSRP~.,train)[,-1]
y <- train$MSRP
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out)
# Look at the coefficient for best lambda
# Make+Model+Year+EngineFuelType+EngineHP+EngineCylinders+TransmissionType+DrivenWheels+NumberOfDoors+VehicleSize+VehicleStyle+HighwayMPG+CityMPG+Popularity+Crossover+Diesel+Exotic+Luxury+HighPerformance+FactoryTurner+Performance+FlexFuel+Hatchback+Hybrid+Yes+N_A
# Lasso turned off some predictors in Make, Model,VehicleStyle... In order to check assumptions, we need to use lm model with all the predictors
# Although this won't imitate the Lasso model perfectly though.
coefficients = coef(cv.out, cv.out$lambda.min)
head(coefficients)
# Compute the final lasso model
lasso.model = glmnet(x,y,alpha = 1,lambda = cv.out$lambda.min)
#Dummy code test set to see performance compare to other methods
xtest<-model.matrix(MSRP~.,test)[,-1]
ytest<-test$MSRP #36302210

# See prediction
lasso.pred=predict(lasso.model ,newx=xtest)
# See test ASE
testMSE_LASSO<-mean((ytest-lasso.pred)^2)
testMSE_LASSO
################
# In order to look at assumption, need to refit the model based on LASSO selected variables...
# Check coefficients and see what got turn off:
# - Crossover (only one turned off, others are within factor levels that are significant)
################
lasso.lm = lm(MSRP~.-Crossover,data=train)
summary(lasso.lm)
# Check Assumptions
par(mfrow=c(2,2))
plot(lasso.lm)
library(olsrr)
ols_plot_cooksd_bar(lasso.lm)
ols_plot_resid_stand(lasso.lm)

##################################################################################
# Try Log(MSRP vs cubic Year & Second degree EngineHP variable selection #########
##################################################################################

# Above are findings during EDA... connections to logMSRP
engineHP.lm = lm(log(MSRP)~EngineHP,data=train)
ols_plot_resid_stand(engineHP.lm)
# Looks like Second degree might help
engineHP.lm2 = lm(log(MSRP)~EngineHP+I(EngineHP^2),data=train)
ols_plot_resid_stand(engineHP.lm2)

#Without transformation
engineHP.lm = lm(MSRP~EngineHP,data=train)
ols_plot_resid_stand(engineHP.lm)
# Looks like Second degree might help, and MSRP looks better than log(MSRP)
engineHP.lm2 = lm(MSRP~EngineHP+I(EngineHP^2),data=train)
ols_plot_resid_stand(engineHP.lm2)

# Try year
year.lm = lm(log(MSRP)~Year,data=train)
ols_plot_resid_stand(year.lm)
# Try Second Degree Year
year.lm2 = lm(log(MSRP)~Year+I(Year^2),data=train)
ols_plot_resid_stand(year.lm2)
# Try Third Degree Year
year.lm3 = lm(log(MSRP)~Year+I(Year^2)+I(Year^3),data=train)
ols_plot_resid_stand(year.lm3)
#Try regular MSRP
# Try year
year.lm = lm(MSRP~Year,data=train)
ols_plot_resid_stand(year.lm)
# Try Second Degree Year
year.lm2 = lm(MSRP~Year+I(Year^2),data=train)
ols_plot_resid_stand(year.lm2)
# Try Third Degree Year
year.lm3 = lm(MSRP~Year+I(Year^2)+I(Year^3),data=train)
ols_plot_resid_stand(year.lm3)
############### Looks like LogMSRP vs year degree 3 helps
############### Looks like LogMSRP vs EngineHP degree 2 helps
# Reselect variables with LASSO
#Dummy code categorical predictor variables
x <- model.matrix(log(MSRP)~.+I(EngineHP^2)+I(Year^2)+I(Year^3),train)[,-1]
y <- log(train$MSRP)
set.seed(123) # Need a seed number to keep same results for LASSO
cv.out2=cv.glmnet(x,y,alpha=1) #alpha=1 performs LASSO
par(mfrow=c(1,1))
plot(cv.out2)
coef(cv.out2, cv.out2$lambda.min)
# Year-Degree2 didn't get turned on neither did I(Year^3), I(EngineHP^2) did get turned on
# Following also get turned off...
# - Hatchback - Popularity 
# Refit the model with predictors
lasso.lm.log = lm(log(MSRP)~.+I(EngineHP^2)-Hatchback-Popularity,data=train)
summary(lasso.lm.log) # R-Squared and Adjusted R-squared is slightly lower compared to regular MSRP using LASSO
# Check Assumptions
par(mfrow=c(2,2))
plot(lasso.lm.log)
library(olsrr)
ols_plot_cooksd_bar(lasso.lm.log)
ols_plot_resid_stand(lasso.lm.log)
#Residual looks okay... check test ASE below

@@

#LASSO test result
lasso.pred2 = predict(lasso.lm,test)
# See LASSO test ASE after refit
testASE_LASSO_2 = mean((test.result-lasso.pred2)^2)
testASE_LASSO_2 #35982124

# LogMSRP with Second Degree EngineHP picked by LASSO test result
lasso.log.pred1 = predict(lasso.lm.log,test)
# Recover the value by exp
lasso.log.pred1 = exp(lasso.log.pred1)
testASE_LASSO_LOG = mean((test.result-lasso.log.pred1)^2)
testASE_LASSO_LOG #24577120
